Learning and comparing functional connectomes between populations

### 2012-12-29 paper.tex
iter
Finish up last part

Most importantly, more complex models can only be estimated to model
interactions between a smaller number of nodes. This is not only due to a
computational difficulty, but also to fundamental roadblocks in
statistics: the complexity of the model must match the richness of the
data. While injecting prior information can help model estimation, the
more informative this prior, the fragile the inference becomes. The
ongoing debate on the impact of hemodynamic lag on Granger-causality
inference \cite{smith2012a} is an example of such fragility.

Diatribe: all model are wrong, but some are useful => a cat is a model of a cat

Setting the cursor between complex models based on a bio-physical
description, and simple phenomenological models such as correlation
matrices. Cite \cite{ravikumar2011} to argue that sparse inverse
covariance is reasonably robust to violations of the assumption of
Gaussianity.

Cross validation \cite{friston2012} to destroy the argument on the
Neyman-Pearson lemma (it is self-confirmatory).

>>>>

Most importantly, more complex models can only be used to model
interactions between a smaller number of nodes. This is not only due to a
computational difficulty, but also to fundamental roadblocks in
statistics: the complexity of the model must match the richness of the
data. While injecting prior information can help model estimation, the
more informative this prior, the fragile the inference becomes. The
ongoing debate on the impact of hemodynamic lag on Granger-causality
inference \cite{smith2012a} is an example of such fragility.
While most of the theory underpinning correlation analysis (Gaussian
graphical models) is based on a Gaussian assumption, the core results
are robust to violations of this assumption \cite{ravikumar2011}.

It is tempting to favor more neurobiologically-inspired models that give
descriptions close to our knowledge of the brain basic mechanisms,
however, as George Box famously said, ``all models are wrong; some models
are useful''. Depending on the question and the data at hand, the cursor
should be set between complex models based on a bio-physical description,
and simple phenomenological models such as correlation matrices. In
particular to model interactions between a large number of regions, as in
full-brain analysis, and learn a large \emph{connectome}, simple models
are to be preferred. For more hypothesis-driven studies, such as the
analysis of the mechanism underlying a specific task, more complex models
can be preferred, if rich data is available. Automatic choice of model is
a difficult problem, however, cross-validation (as used in
\cite{varoquaux2010c,craddock2011,strother2006}) is a useful tool. The
central principle of cross-validation is to learn (or fit) a model, and
then test its test predictive power on unseen data. Models too complex
for the data available while fit noise in the data, and thus generalize
poorly. The main benefit of cross-validation is that it is a
non-parametric method which does not rely strongly on modeling
assumption\footnote{This is to be contrasted to Bayesian model
comparison, which will give correct results only if the true generative
model is in the list of models compared. \cite{friston2012} argues that,
based on the Neyman-Pearson lemma, cross-validation is less powerful than
likelihood ratio tests relying on the full dataset. However, it is
important to keep in mind that these approaches only test for
self-consistence, as they require that model likelihood to describe the
data well.}.
